Title of the document here

### 2015-01-26 rmtw/assignment_1/assignment_1.tex
First draft of the purpose section

*Purpose statement (concise  and clear)  leading into  RQ(s)
 -i.e.  describe  the purpose of  your  survey/questionnaire

@@

%------------------------------------------------------------------------- 
\SubSection{Methodology}

>>>>

%Introduction, specifying why this is urgent, needed etc from the notes above

 The purpose of this survey study is therefore to test the theory that the readability differences between computer programming languages affects the given languages suitability for teaching.

 The Independent variables will be defined as the experience, age, preferred language, least preferred language and the working language of the participant. The dependent variables, appeal and suitability, will highlight the relationship between the independent and dependent variables.

 The survey data will be collected from professionals, teachers, students and hobbyists via a series of on-line surveys. The respondents will then be asked to review a series of code snippets from popular languages and will be subsequently asked to rate their readability.

 The data will highlight the readability of the languages and combined with their roles will allow us to make suggestions as to where these languages would be most suitable.

@@

What are the measurable differences in readability between programming languages.

How do the measurable differences between languages correlate to their use in academia for teaching?

How do the measurable differences between languages correlate to the popularity of the language 
%------------------------------------------------------------------------- 
\SubSection{Methodology}
